
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Focus Beamer Presentation
% LaTeX Template
% Version 1.0 (8/8/18)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Pasquale Africa (https://github.com/elauksap/focus-beamertheme) with modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% Template license:
% GNU GPL v3.0 License
%
% Important note:
% The bibliography/references need to be compiled with bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{beamer}

\beamertemplatenavigationsymbolsempty % suppress navigation bar

\usetheme{default} % Use the Focus theme supplied with the template
% Add option [numbering=none] to disable the footer progress bar
% Add option [numbering=fullbar] to show the footer progress bar as always full with a slide count

% Uncomment to enable the ice-blue theme
%\definecolor{main}{RGB}{92, 138, 168}
%\definecolor{background}{RGB}{240, 247, 255}

%------------------------------------------------

\usepackage{booktabs} % Required for better table rules

\begin{document}

\begin{frame}{Midterm Practice}
On the front page of the 9.23.19 edition of the newspaper USA Today one reads: \textit{``Dairy Farmers weigh drop in milk drinkers. Consumption declines in favor of soy, almond and other ‘fake’ milks."}  Assume the market for cows’ milk produced by dairy farmers approximates the model of perfect competition. 
\begin{enumerate}
\item What is the likely effect of the “drop” in the number of “milk drinkers” on the market price of milk and the market quantity?
\item If the market demand for milk is elastic, what is the likely effect of the “drop in milk drinkers” on the total revenue going to milk producers (i.e., dairy farmers)?
\item Given this trend in milk consumption, what is the likely effect on the number of milk producers?
\item What is the likely effect of the “drop in milk drinkers” on the price of yogurt products (cows’ milk being an input for yogurt production)?
\end{enumerate}
\end{frame}

\begin{frame}{Midterm Practice}
On the front page of the 9.23.19 edition of the newspaper USA Today one reads: \textit{``Dairy Farmers weigh drop in milk drinkers. Consumption declines in favor of soy, almond and other ‘fake’ milks."}  Assume the market for cows’ milk produced by dairy farmers approximates the model of perfect competition. 
\begin{enumerate}
\setcounter{enumi}{4}
\item If the U.S. Department of Agriculture determines that milk prices are “too low” to be fair for dairy farmers and “supports” the price of milk at a level higher than the market clearing (or equilibrium) price, what is the economic consequence of the price support?
\item What are two policy measures the government might take to make the milk price support effective?
\item What is the likely effect of the drop in the consumption of cows’ milk on the price of what the article calls “soy, almond and other ‘fake’ milks”?
\end{enumerate}
\end{frame}

\begin{frame}{Midterm Practice}
Define the following:
\begin{itemize}
\item Pareto optimality
\item Income elasticity of demand
\item Perfectly  inelastic demand curve
\item Search or transaction costs
\end{itemize}
\end{frame}





\end{document}
