%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Welcome to Overleaf --- just edit your LaTeX on the left,
% and we'll compile it for you on the right. If you open the
% 'Share' menu, you can invite other users to edit at the same
% time. See www.overleaf.com/learn for more info. Enjoy!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{exam}

\lhead{ECON 2010}
\chead{Problem Set \#1}
\lfoot{}
\rhead{Fall 2022}

\begin{document}

%\vspace{5mm}
%\makebox[0.75\textwidth]{Name and section:\enspace\hrulefill}

%\vspace{5mm}
%\makebox[0.75\textwidth]{Instructor’s name:\enspace\hrulefill}

\section{Graded Questions}

Write up your answers and submit a physical copy during discussion on the due date. Please label the following on your graphs: the axes ($P$ and $Q$), supply and demand ($S$ and $D$), and the equilibrium point (either labelling the point with $E$ or using dotted lines to show the price and quantity). This is a good habit, and will be a requirement on the midterms. \\

\begin{questions}
\question A classmate has a monthly allowance from her family of \$500 which she spends on bagels and textbooks. 

\begin{parts}
\part Sketch your classmate's PPC with dollars of bagels on the $x$-axis and dollars of textbooks on the $y$-axis. 
%\vspace{3.5in}
\part Suppose that the price of a bagel doubles due to supply chain problems. Sketch the new PPC on your graph.
\part The student decides to save \$100 each month towards paying off her student debt. Explain how this would change the PPC.
%\vspace{1in}
\part Is this PPC linear or concave? Why?
\end{parts}

\question Consider the market for vacation home rentals in the Outer Banks, North Carolina.
\begin{parts}
\part Suppose that the equilibrium price for a week-long rental is \$1,000. Sketch possible supply and demand curves.
\part Part of the Outer Banks slides into the ocean, destroying several vacation homes and lowering supply. Illustrate this event on the graph.
\part Suppose that the rental price initially stays at \$1,000 after the shock from (b). Is there a shortage or surplus? Identify the magnitude of the shortage/surplus on the graph. 
\part Eventually, the market reaches a new equilibrium. What is the ultimate effect of the supply shock on the price and quantity of vacation rentals?
\end{parts}

\question Faster rendering algorithms have led to dramatic improvements in the supply of virtual reality (VR) games.
\begin{parts}
\part Prior to these improvements, there is no market for VR games. Draw a graph of supply and demand curves which represent a nonexistent market (Hint: your curves will not intersect). Use the graph to illustrate the result of a positive supply shock on the equilibrium price and quantity of VR games.
\part Suppose that desktop computers are complements for VR games. Use another graph to show how changes in the price of VR games is likely to affect the desktop market.
\part Repeat part (b) with a substitute to VR games.
\part An industry analyst asks you to help determine whether VR games are normal or inferior goods. What information will you need to help the analyst?
\end{parts}

\end{questions}

\section{Extra Practice (ungraded)}

\begin{questions}
\question A school chooses whether to penalize parents who pick up their children late with a lump sum fee of \$25 or a per-minute fee of \$2.
\begin{parts}
\part One parent has a total daily income of \$100. Sketch his PPC with dollars on the y-axis and minutes of childcare on the x-axis if the school chooses the per-minute fee.
\part What does this PPC look like if the school chooses the lump-sum fee?
\end{parts}

\question This question examines the connection between the Law of Demand and market equilibrium.
\begin{parts} 
\part Suppose that demand for a designer perfume violates the Law of Demand over the range of quantities $[100, 200]$ and that it satisfies the law everywhere else. Sketch  a graph of this demand curve.
\part Draw an upward-sloping supply curve that intercepts the demand curve three times.
\part What can you say about the equilibrium price and quantity in this market?
\end{parts}
\end{questions}

\end{document}