%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Welcome to Overleaf --- just edit your LaTeX on the left,
% and we'll compile it for you on the right. If you open the
% 'Share' menu, you can invite other users to edit at the same
% time. See www.overleaf.com/learn for more info. Enjoy!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{exam}

\lhead{ECON 2010}
\chead{Problem Set \#3}
\lfoot{}
\rhead{Fall 2022}

\begin{document}

\section{Graded Questions}

\begin{questions}

\question A consumer has the utility schedules for doughnuts and muffins listed below.

\begin{parts} 
\part Complete the tables if the price of doughnuts is \$4 and the price of muffins is \$3.

\vspace{1em}

\begin{large}
\begin{tabular}{ |l|l|l|l| } 
\hline
Doughnuts & Total Utility & Marginal Utility & MU / P \\
 \hline
 0 & 0 & --- & --- \\ \hline
 1 & 12 & & \\ \hline
 2 & 20 & & \\ \hline
 3 & 24 & & \\ \hline
 4 & 26 & & \\ \hline
\end{tabular}

\vspace{1em}

\begin{tabular}{ |l|l|l|l| } 
\hline
Muffins & Total Utility & Marginal Utility & MU / P \\
 \hline
 0 & 0 & --- & --- \\ \hline
 1 & 15 & & \\ \hline
 2 & 27 & & \\ \hline
 3 & 33 & & \\ \hline
 4 & 36 & & \\ \hline
\end{tabular}
\end{large}
\vspace{1em}

\part What bundle of doughnuts and muffins will the consumer purchase if her total income is \$17?
\end{parts}

\question
Draw a supply and demand graph and label the consumer surplus. Why is it located where you’ve drawn it?

\question
70-year-old retiree and international pop sensation Taylor Swift both board the same flight from New York to Nashville. Each flies business class and orders the same meal and drinks, the bill ends up being around \$800. Who has the higher accounting cost in this situation? Who has a higher economic cost?

\question
You are the owner and only chef for an Italian restaurant on the Charlottesville Downtown Mall. Each month, you pay your wait staff \$5,000 in wages, spend \$3,000 on raw ingredients, and \$2,000 on rent since you don’t own the building. You turn a revenue of \$12,000 each month and pay yourself whatever remains of that after paying for everything else. You also know that if you abandoned the venture and instead started working at Olive Garden, you would be paid \$3000 per month. What are your accounting costs in this situation? What about economic costs? Should you keep your restaurant open?


\end{questions}


\end{document}